Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of Strategies in the Moran process for the Iterated Prisoner's Dilemma

### 2018-07-17 main.tex
Fix a strange par indent.

When $N=2$ the fixation probabilities of the Moran process are effectively measures
of the distribution of  relative
mean payoffs over all possible matches between two players. The strategy
that scores higher than the other more often will fixate more often. For \(N=2\)
the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
considered separately for larger \(N\) in the following sections.
The top 16 (10\%) strategies are
shown in

Table~\ref{tbl:summary_top_2} and figures showing the performance of all
strategies are available in the appendix.
The top five ranking strategies are:

>>>>

When $N=2$ the fixation probabilities of the Moran process are effectively
measures of the distribution of  relative mean payoffs over all possible matches
between two players. The strategy that scores higher than the other more often
will fixate more often. For \(N=2\) the two cases of \(x_1\) and \(x_{N-1}\)
coincide, but will be considered separately for larger \(N\) in the following
sections.  The top 16 (10\%) strategies are shown in
Table~\ref{tbl:summary_top_2} and figures showing the performance of all
strategies are available in the appendix.  The top five ranking strategies are:
